\begin{abstract}
    Agility plays a big role in managing the complexity of volatile and unpredictable environments, such as project management and project portfolio management, by focussing on the value created for the customer. This leads to the need of systematically scaling agile practices to enterprise level, which can be done by using e.g. the Scaled Agile Framework (SAFe) or Flight Levels and results in big organizational structures with multiple levels of planning and decision making, which have to be documented.
    \newline
    \newline
    For effective decision making in those environments, decisions should be made with metrics in mind that are relevant for the Level in which the decision must be made. This work presents a customizable software solution to document the organizational structure in a way that allows automatic aggregation of such metrics to the level required. These Metrics should be presented in a meaningful manner, providing insights on progress from levels below the one where the decision must be made in and what implications the decision will have on the levels above. Focus of this work is the adaptability of the solution regardless of the framework used to scale agile practices.
    \newline
    \newline
    The solution was evaluated in a case study to determine its usefulness as a webbased software. The results show that the adaptability of the solution is given, but to be useful in a real world scenario, the solution needs to be extended with time-based metrics like velocity, etc. and the ability to not only import data from operational tools like Jira, but also a synchronization of data between the tools, to make the solution usable over time, since the data only represents a snapshot of the current state of the organization.
    \newline
    \newline
    \textbf{Keywords:} agile portfolio management, agile project management, progress tracking, decision making, Flight Levels, Scaled Agile Framework, data aggregation, visualization, web development, mevn stack
\end{abstract}
